---
title: "R Markdown and Leaflet"
author: "Edward Cheng"
date: "November 23, 2016"
output: html_document
always_allow_html: yes
---

## Introduction

Leaflet is one of the most popular Javascript libraries for
creating interactive maps. The leaflet R package allows you
to create your own leaflet maps without needing to know any
Javascript!

### Installation

```r
install.packages("leaflet")
```

## My First Map

Getting started with leaflet is easy. The `leaflet()`
function creates a map widget that you can store in a
variable so that you can modify the map later on. You can
add features to the map using the pipe operator (`%>%`) just
like in dplyr. The `addTiles()` function adds mapping data
from [Open Street Map](http://www.openstreetmap.org/).

```{r, eval=FALSE}
library(leaflet)
my_map <- leaflet() %>% 
  addTiles()
my_map
```

## My First Map

```{r, echo=FALSE}
library(leaflet)
my_map <- leaflet() %>% 
  addTiles()
my_map
```

## Adding Markers

You can add markers to your map one at a time using the
`addMarkers()` function by specifying the longitude and
latitude. ([Here's](https://twitter.com/drob/status/719927537330040832)
a tip if you tend to mix them up.) You can specify popup
text for when you click on the marker with the `popup` 
argument.

```{r, eval=FALSE}
library(leaflet)
my_map <- my_map %>%
  addMarkers(lat=25.03374, lng=121.56480, 
             popup="Taipei 101 Building")
my_map
```

## Adding Markers

```{r, echo=FALSE}
library(leaflet)
my_map <- my_map %>%
  addMarkers(lat=25.03374, lng=121.56480, 
             popup="Taipei 101 Building")
my_map
```

## Mapping Clusters

Sometimes you might have so many points on a map that it
doesn't make sense to plot every marker. In these situations
leaflet allows you to plot clusters of markers using
`addMarkers(clusterOptions = markerClusterOptions())`. When
you zoom in to each cluster, the clusters will separate until
you can see the individual markers.

```{r, eval=FALSE}
df <- data.frame(lat = runif(500, min = 24.98, max = 25.08),
                 lng = runif(500, min = 121.51, max = 121.61))
df %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers(clusterOptions = markerClusterOptions())
```

## Mapping Clusters

```{r, echo=FALSE}
df <- data.frame(lat = runif(500, min = 24.98, max = 25.08),
                 lng = runif(500, min = 121.51, max = 121.61))
df %>% 
  leaflet() %>%
  addTiles() %>%
  addMarkers(clusterOptions = markerClusterOptions())
```

## Conclusion

For more details about the leaflet package for R 
visit http://rstudio.github.io/leaflet/.

